Poker Chips, Earthquakes, and Computation

### 2014-10-13 finaldraft.tex
added haikus

\section{Poem}

\begin{quote}
A board with chips.\\
An earthquake redistibutes some chips.\\
New board! never turn back. \\ \\

Another earthquake hits.\\
And another earthquakes hits again.\\
Who cares which first! \\ \\

One last earthquake\\
So many it must be Japan.\\
Computation.
\end{quote}
\end{document}

>>>>

\section{Three Haikus}

Poker board with chips\\
Suddenly hit by earthquakes.\\
Can never return. \\

\noindent Another earthquake\\
hits the board, and then one more\\
Who cares which was first! \\

\noindent Now the aftershock\\
is computing some functions,\\
but just basic ones.
\end{document}
